Minicaml, a purely functional, didactical programming language\\WORK IN PROGRESS DRAFT

### 2020-01-07 paper/paper.tex
paper

%% Language and font encodings. This says how to do hyphenation on end of lines.
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{xcolor}
%\usepackage{tgpagella} % text only
\usepackage{mathpazo}
\usepackage{multicol}
\setlength{\columnsep}{1.5cm}
\setlength{\columnseprule}{0.5pt}
%\usepackage{aas_macros}

@@

\newcommand{\te}[1]{\text{#1}}

@@

\textbf{Dictionaries}\\
Note that the evaluation step of the dictionary is considered implicit.

\begin{gather*}
	\te{Insertion} \\
	\hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow
	\te{true}}{<\te{env, insert k v dict}> \Rightarrow \te{dict} \cup (\te{k,v})} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, insert k v dict}> \Rightarrow \te{dict}} \\ \\
	\te{Deletion} \\ \hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, remove k dict}> \Rightarrow \te{dict} \textbackslash \{(\te{k,v})\}} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, remove k dict}> \Rightarrow \te{error}} \\ \\
	\te{Contains key} \\ \hline \\
	<\te{env}, \te{haskey k dict}> \Rightarrow \te{k} \in \te{dict} \\ \\
	\te{Retreive a value} \\ \hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, getkey k dict}> \Rightarrow \te{v}} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, getkey k dict}> \Rightarrow \te{error}} \\ \\
	\te{Filter by keys} \\ \hline \\
	\dfrac{<\te{env, ks}> \Rightarrow \te{\{k1, ..., kn\}}}{<\te{env, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{d} \mid (k \in ks) \}} \\ \\
	\te{Map} \\ \hline \\
	\dfrac{<\te{env, f}> \Rightarrow \lambda(x)}{<\te{env, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{d}  \}} \\ \\
	\te{Fold Left} \\ \hline \\
	\dfrac{\begin{aligned}
		<\te{env, f}> \Rightarrow \lambda(x,y)  \\
		<\te{env, d}> \Rightarrow \{(k_1, v_1), \hdots, (k_n, v_n)\}
	\end{aligned}}{<\te{env, foldl f a d}> \Rightarrow \lambda( \hdots \lambda(\lambda(a, v_1), v_2), \hdots, v_n)} \\ \\
\end{gather*}

>>>>

%% Language and font encodings. This says how to do hyphenation on end of lines.
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{collectbox}
%\usepackage{tgpagella} % text only
\usepackage{mathpazo}

\usepackage{multicol}
\setlength{\columnsep}{1.5cm}
\setlength{\columnseprule}{0.5pt}
%\usepackage{aas_macros}

@@

\newcommand{\te}[1]{\text{#1}}
\newcommand{\mybox}{%
    \collectbox{%
        \setlength{\fboxsep}{1pt}%
        \fbox{\BOXCONTENT}%
    }%
}

@@

\textbf{Dictionaries}\\
Note that the evaluation step of the dictionary is considered implicit in most
cases. Primitives require that the arguments passed are already evaluated,
therefore dictionaries are considered already evaluated. An exception is made
for the \textit{Fold Left} catamorphism, where the key-value couples have
to be enumerated in order to show the set-theoretic representation of a left fold.

\begin{gather*}
	\te{Insertion} \\
	\hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow
	\te{true}}{<\te{env, insert k v dict}> \Rightarrow \te{dict} \cup (\te{k,v})} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, insert k v dict}> \Rightarrow \te{dict}}
\end{gather*}
\begin{gather*}
	\te{Deletion} \\ \hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, remove k dict}> \Rightarrow \te{dict} \textbackslash \{(\te{k,v})\}} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, remove k dict}> \Rightarrow \te{error}}
\end{gather*}
\begin{gather*}
	\te{Contains key} \\ \hline \\
	<\te{env}, \te{haskey k dict}> \Rightarrow \te{k} \in \te{dict}
\end{gather*}
\begin{gather*}
	\te{Retreive a value} \\ \hline \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{true}}{<\te{env, getkey k dict}> \Rightarrow \te{v}} \\ \\
	\dfrac{<\te{env, k} \in \te{dict}> \Rightarrow \te{false}}{<\te{env, getkey k dict}> \Rightarrow \te{error}}
\end{gather*}
\begin{gather*}
	\te{Filter by keys} \\ \hline \\
	\dfrac{<\te{env, ks}> \Rightarrow \te{\{k1, ..., kn\}}}{<\te{env, filterkeys ks d}> \Rightarrow \{ (k, v) \in \te{d} \mid (k \in ks) \}}
\end{gather*}
\begin{gather*}
	\te{Map} \\ \hline \\
	\dfrac{<\te{env, f}> \Rightarrow \lambda(x)}{<\te{env, map f d}> \Rightarrow \{ (k, \lambda(v)) \mid (k, v) \in \te{d}  \}}
\end{gather*}
\begin{gather*}
	\te{Fold Left} \\ \hline \\
	\dfrac{\begin{aligned}
		<\te{env, f}> \Rightarrow \lambda(x,y)  \\
		<\te{env, d}> \Rightarrow \{(k_1, v_1), \hdots, (k_n, v_n)\}
	\end{aligned}}{<\te{env, foldl f a d}> \Rightarrow \lambda( \hdots \lambda(\lambda(a, v_1), v_2), \hdots, v_n)} \\ \\
\end{gather*}
